Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-26 paper/main.tex
Update DTA prediction scores table

	\begin{tabular}{|l|l|r|r|r|}
		\hline
		Approach&Splitting scheme&Original AUROC score&Protein split AUROC&MicroAUC\\
		\hline
		DTINet&DP pairs&$91$&$84.1$&$67.2$\\
		DTIGEMS+&DP pairs&$93$& $72.2$& $67.8$ \\
		DTI-CDF&Proteins&$83$&$83$&$79$\\
		GNN-DTI&&&&\\
		\hline
		MolTrans&&&&\\
		GraphData&&&&\\
		\hline
	\end{tabular}
	\item A naive predictor (ranking proteins) and predict each drug similarly achieves cutting edge performance ($87.5$ AUROC for whole dataset, $85.5$ for 5-fold cross validation in drug-split) $\rightarrow$ No prot focused microAUC possible. $\rightarrow$ hub proteins
	\item Yamanishi Dataset is only partially suitable, if everybody just derives a suitable subset (DTIGEMS)
\end{itemize}

>>>>

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|r|}
		\hline
		Approach&Splitting scheme&Original AUROC score&Protein split AUROC&MicroAUC\\
		\hline
		DTINet&DP pairs&$91$&$84.1$&$67.2$\\
		DTIGEMS+&DP pairs&$93$& $72.2$& $67.8$ \\
		DTI-CDF&Proteins&$83$&$83$&$79$\\
		\hline
	\end{tabular}
	\item A naive predictor (ranking proteins) and predict each drug similarly achieves cutting edge performance ($87.5$ AUROC for whole dataset, $85.5$ for 5-fold cross validation in drug-split) $\rightarrow$ No prot focused microAUC possible. $\rightarrow$ hub proteins
	\item Yamanishi Dataset is only partially suitable, if everybody just derives a suitable subset (DTIGEMS)
	\item This also applies to drug target affinity prediction. We were hereby able to roughly reproduce the results from MolTrans (Bioinformatics) on BioSnap

\end{itemize}

\begin{figure}[!tpb]%figure1
	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|r|}
		\hline
		Approach&Splitting scheme&Original AUROC score&Protein split AUROC&MicroAUC\\
		\hline
		DeepDTI&Drugs&$87.6$&$75.9$&$70.1$\\
		DeepDTA&DP pairs&87.6&$76.7$&$69.4$\\
		DeepConv-DTI&DP pairs&88.3&$76.6$&$73.0$\\
		MolTrans&DP pairs&89.5&$77.0$&$74.0$\\

		\hline
	\end{tabular}
\end{figure}
